manuscript_figures

### 2024-05-29 scripts/manuscript_figures.Rmd
finished data and figure 2

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

# Aggregate the data by year, site, and transect and compute mean values
aggregated_data <- merged.dat %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(mean_fish_biomass = mean(Fish.Biomass..g.m2., na.rm = TRUE),
            mean_kelp_cover = mean(COVER, na.rm = TRUE)) %>%
  ungroup()

# Perform linear regression
lm_model <- lm(mean_fish_biomass ~ mean_kelp_cover, data = aggregated_data)
lm_summary <- tidy(lm_model)
lm_summary_stats <- summary(lm_model)  # Get model summary

# Extract R-squared and p-value
r_squared <- round(lm_summary_stats$r.squared, 2)
p_value <- signif(lm_summary$p.value[2], 2)

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  annotate("text", x = Inf, y = Inf, label = paste0("R^2 = ", r_squared, ", p = ", p_value), 
           hjust = 2, vjust = 4, size = 4, parse = FALSE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_classic(); figure.2

@@

>>>>

# Load libraries 
```{r}
library(plyr)
library(dplyr)
library(MuMIn)
library(tidyverse)
library(lme4)
library(broom.mixed)
library(lubridate)
library(ggplot2)
library(patchwork)
library(broom)

@@

# Fit the linear mixed effects model
lmm_model <- lmer(mean_fish_biomass ~ mean_kelp_cover + SITE + (1 | SITE/YEAR), data = aggregated_data)

# Summarize the model
lmm_summary <- summary(lmm_model)
lmm_tidy <- tidy(lmm_model)

# Calculate R-squared for the mixed model
r_squared <- r.squaredGLMM(lmm_model)

# Extract marginal and conditional R-squared
marginal_r2 <- round(r_squared[1], 2)
conditional_r2 <- round(r_squared[2], 2)
p_value <- signif(lmm_tidy$p.value[lmm_tidy$term == "mean_kelp_cover"], 2)

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  annotate("text", x = Inf, y = Inf, label = paste0("Marginal R^2 = ", marginal_r2, "\nConditional R^2 = ", conditional_r2, "\np = ", p_value), 
           hjust = 1.1, vjust = 1.1, size = 4, parse = FALSE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_classic();figure.2

@@

# Figure 3: Make the saame regression figure for fish biomass and kelp biomass (g/m2). To get kelp biomass, you will use the quad data which counts the number of kelp blades, and convert to biomass using the morphometric data. Take stipe length, blade width, blade length and convert to biomass. Then get a mean and SE of kelp frond biomass at that transect and multiply that by the number of fronds counted in quad. We want units to be g/m2 (I think).
